Cities as they could be: Artificial Life and Urban Systems

### 2020-02-16 Docs/Papers/ALifeCities/paper.tex
init_corpus_constr

\title{Cities as they could be: an Artificial Life approach to Urban Systems}
\author{Juste Raimbault$^{1,2,3}$\\
\mbox{}\\
$^1$Center for Advanced Spatial Analysis, University College London\\
$^2$UPS CNRS 3611 ISC-PIF\\
$^3$UMR CNRS 8504 G{\'e}ographie-cit{\'e}s
juste.raimbault@polytechnique.edu} % email of corresponding author

@@

@@

>>>>

\title{Cities as they could be: Artificial Life and Urban Systems}
\author{Juste Raimbault$^{1,2,3}$\\
\mbox{}\\
$^1$Center for Advanced Spatial Analysis, University College London\\
$^2$UPS CNRS 3611 ISC-PIF\\
$^3$UMR CNRS 8504 G{\'e}ographie-cit{\'e}s
juste.raimbault@polytechnique.edu} % email of corresponding author

@@

\cite{batty2009centenary} % + relevant in other paper: morphogenesis, urban evolution?

@@

The keyword request follows \cite{niu2016global} and uses only \texttt{Artificial Intelligence AND Urban} for AI approaches and \texttt{Artificial Life AND Urban} for ALife. Using alternative terms such as ``machine learning'' or ``city'' expands the scope too much and yield non relevant results.
% "smart city" ok should come by itself in the scope - less a priori as possible
We construct initial seed corpuses using these requests
% 20 limit already fine for ALife
% -> add by hand refs? such as \cite{kato1998alife}
% AI: start with 50 - seems relevant up to 100 at least but strong intersection with CA approaches.
%
